---
title: "On Radiohead"
subtitle: ""
author: 
  - Richard Guo
  - Maryam Ansari
  - Gauravpreet Thind
thanks: "Code and data are available at: https://github.com/amayyam/spotify_artist_analysis"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
radiohead <- readRDS(here::here("data/02-analysis_data/analysis_data.rds"))
```


# Acknowledgements
We used the statistical programming language R [@citeR] to conduct analysis. Our data was taken from [@spotify] using their developer API. Parts of the code were written with the assistance of  @tellingstories and @CGPT.

# Data
Radiohead are an English rock band that is sometimes played on alternative radio stations in Toronto, such as 102.1 and 107.1. According to the play statistics on their Spotify page, their five most popular songs are 'Creep', 'No Surprises', 'Karma Police', 'High and Dry', and 'Jigsaw Falling Into Place' in descending order. @fig-valence shows the perceived happiness of Radiohead songs, as rated by many MIT undergraduate students. 

```{r}
#| echo: false
#| warning: false
#| fig-cap: Valence of Radiohead songs
#| label: fig-valence
radiohead |>
  select(album_release_date, valence) |>
  mutate(album_release_date = ymd(album_release_date)) |> 
  ggplot(aes( x = album_release_date, y = valence)) +
  geom_point(alpha = 0.3) +
  geom_smooth() +
  theme_minimal() +
  labs(
   x = "Album release date",
   y = "Valence",
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```


\newpage


# References


