---
title: "Radiohead"
subtitle: ""
author: 
  - Richard Guo
  - Maryam Ansari
  - Gauravpreet Thind
thanks: "Code and data are available at: https://github.com/amayyam/spotify_artist_analysis"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```


# Introduction
Radiohead are an English rock band that is sometimes played on alternative radio stations in Toronto, such as 102.1 and 107.1. According to the play statistics on their spotify page, their most popular song is 'Creep'.  

```{r}
#| echo: false
radiohead |>
  select(artist_name, album_release_date, valence) |>
  mutate(album_release_date = ymd(album_release_date)) |> 
  ggplot(aes( x = album_release_date, y = valence, color = artist_name)) +
  geom_point(alpha = 0.3) +
  geom_smooth() +
  theme_minimal() +
  facet_wrap(facets = vars(artist_name), dir = "v") +
  labs(
   x = "Album release date",
   y = "Valence",
   color = "Artist"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```


# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@spotify].... Following @tellingstories, we consider...

Overview text

## Measurement
	
Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Talk way more about it. 

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.








# Results



# Discussion
# Appendix
\newpage


# References


